Appendix

### 2019-07-15 manuscript/appendix.Rmd
transparent waffle background

ggplot(tidyr::gather(dt, key = "key", value = "value", -`Trophic State`),
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=1.125, n_rows = 7) +
  facet_wrap(~key, ncol=1) +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0)) +
  ggthemes::scale_fill_tableau(name=NULL) +
  coord_equal() +
  labs(title = "Trophic State")  +
#   theme_ipsum_rc(grid="") +
   theme_enhance_waffle() + 
  theme(strip.background = element_blank())

>>>>

ggplot(tidyr::gather(dt, key = "key", value = "value", -`Trophic State`),
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=1.125, n_rows = 7) +
  facet_wrap(~key, ncol=1) +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0)) +
  ggthemes::scale_fill_tableau(name=NULL) +
  coord_equal() +
  labs(title = "Trophic State")  +
#   theme_ipsum_rc(grid="") +
   theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"))
